Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 6

    %The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
    %massive galaxies are consistent with the two-phase formation scenario. 
    \jenny{We find that the outer halos of massive elliptical galaxies grow more prominent and 
    more elliptical with increasing stellar mass.}
    According to this theory, the ``cores'' \jenny{specify 5-10 kpc is meant?} of massive central galaxies are formed 
    at $z{\sim} 2$ during an intense period of \textit{in situ} star formation. 
    The outskirts of massive galaxies are then built up through a more gradual second 
    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
    accretion and merger.
    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
    outskirts of the centrals and do not have a large impact on the central \mden{} 
    profile (e.g. \citealt{Oogi2013, Bedorf2013}). \jenny{Mike BK \& Ma paper too.}
    Given the stochastic nature of the merging process, it is easy to understand why 
    the \mden{} profiles of massive galaxies are similar in the inner region but show
    large and continuous scatter in the outskirt. \jenny{do not understand what continuous 
    scatter means?}

>>>>

    %The mass-dependent nature we find in the \mden{} and ellipticity profiles of 
    %massive galaxies are consistent with the two-phase formation scenario. 
    We find that the outer halos of massive elliptical galaxies grow more prominent and 
    more elliptical with increasing stellar mass.
    According to the two-phase formation scenario, the inner 5--10 kpc of these 
    massive central galaxies are formed at $z>1$ during an intense period of 
    \textit{in situ} star formation. 
    The outskirts of massive galaxies are then built up through a more gradual second 
    phase of evolution (the \textit{ex situ} phase) that is dominated by mass assembly via 
    accretion and merger.
    Non-dissipative mergers, especially the minor ones, mostly deposit stars in the 
    outskirts of the centrals and do not have a large impact on the central \mden{} 
    profile (e.g. \citealt{Oogi2013, Bedorf2013}). \jenny{Mike BK \& Ma paper too.}
    Given the stochastic nature of the merging process, it is easy to understand why 
    the \mden{} profiles of massive galaxies are similar in the inner region but show
    large and continuous scatter in the outskirt.
